Supplementary Information

### 2020-08-28 doc/manuscript/MEE_manuscript_SI.Rmd
complete table S4

## Table S3. Sampling details for species by site
(**[ISSUE #73 in ForestGEO-climate-sensitivity ](https://github.com/EcoClimLab/ForestGEO-climate-sensitivity/issues/73)

@@

(**[ISSUE #71 in ForestGEO-climate-sensitivity ](https://github.com/EcoClimLab/ForestGEO-climate-sensitivity/issues/71)

\newpage
## Table S4. Frequency of $DBH$-climate interactions across all sites and growth metrics
```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
table_raw <- read.csv("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/climate_interactions_summary.csv", stringsAsFactors = FALSE, check.names = FALSE)
#this reads in the table, but knit fails if I try to render it (probably because of underscores). It also needs ot be rearranged
#kable(table_raw, format = "latex", booktabs = TRUE, caption = "Table S  . Frequency of DBH-climate interactions", escape = F)%>%
#  kable_styling(latex_options = c("scale_down", "hold_position")) 
```

>>>>

## Table S3. Sampling details for species by site
*([ISSUE #73 in ForestGEO-climate-sensitivity ](https://github.com/EcoClimLab/ForestGEO-climate-sensitivity/issues/73))*

@@

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
allometries_table <- read.csv("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO_dendro/data_processed/dbh_to_bark_allometries_table.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(allometries_table, format = "latex", booktabs = TRUE,   escape = F, linesep = c('\\addlinespace'))%>%
  column_spec(1, italic = T) %>%
  column_spec(5, width = "3cm") %>%
  column_spec(6, width = "6cm") %>%
  row_spec(0, italic = F, bold = T) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), protect_latex = T) 
```

\newpage
## Table S5. Frequency of $DBH$-climate interactions across all sites and growth metrics
```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
table_raw <- read.csv("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/climate_interactions_summary.csv", stringsAsFactors = FALSE, check.names = FALSE)
#this reads in the table, but knit fails if I try to render it (probably because of underscores). It also needs ot be rearranged
#kable(table_raw, format = "latex", booktabs = TRUE, caption = "Table S  . Frequency of DBH-climate interactions", escape = F)%>%
#  kable_styling(latex_options = c("scale_down", "hold_position")) 
```
